
%	Acknowledgments

\thispagestyle{empty}

\vspace*{\stretch{1}}
\begin{center}
%	{\LARGE\bfseries \textcolor{white}{ACKNOWLEDGMENTS}}
	{\LARGE\bfseries ACKNOWLEDGMENTS}
\end{center}
\vs\hs
I would like to express my gratitude to many people for their guidance and encouragement as I carried out this study.\\
\hs
My supervisor, Prof.~Yusuke~Koshio, was very encouraging to me.
Even though he was busy, he was always concerned about my study and gave me a lot of advice on how to proceed with my study smoothly.
He also taught me the importance of having a strong own will and not being influenced by other people's opinions.
I have been able to come this far because of his support, and I would like to apply what I have learned so far to my life in the future.
If we have a chance, let's go for a drink again!\\
\hs
I would also like to express my gratitude to my co-researchers for their help on various situations.
Prof.~Masayuki~Nakahata, Prof.~Hiroyuki~Sekiya, Dr.~Motoyasu~Ikeda, Dr.~Kei~Ieki, and Dr.~Keishi~Hosokawa were very helpful during the gadolinium-loading work.
Prof.~Yoshinari~Hayato and Dr.~Seisho~Abe were very kind to teach me about the simulation for neutrino interactions.
Dr.~Takatomi~Yano and Dr.~Yuuki~Nakano helped me with the Super-Kamiokande detector simulation development and data analysis.
Prof.~Teppei~Katori, Prof.~Yasuhiro~Nakajima, Dr.~Volodymyr~Takhistov, Dr.~Linyan~Wan, Prof.~Mark~Vagins, Prof.~Kate~Scholberg, Prof.~Luis~Labarga, Dr.~Ryosuke~Akutsu, Dr.~Yosuke~Ashida, and Dr.~Hiroshi~Ito gave me a lot of comments and advice when I was writing my paper (S.~Sakai \textit{et al}., Phys. Rev. D \textbf{109}, L011101 (2024)).
My colleagues, Shota~Izumiyama, Masataka~Shinoki, and Seungho~Han, gave me great inspiration as I proceeded my study.\\
\hs
I would also like to thank the members of the Particle Physics Laboratory at Okayama University for their help and support.
My seniors, Dr.~Yota~Hino and Dr.~Masayuki~Harada, helped me in various aspects of my study.
Thanks to my juniors, Fumi~Nakanishi, Yuki~Shiraishi, Tomoaki~Tada, Tomohiro~Tano, Koyo~Takeya, Kouki~Hamaguchi, Akinori~Higashi, Mei~Homma, and Nozomu~Meguro, my research life has become more enjoyable.
The office manager, Rie~Yamamoto, helped me with business trips and paperwork.
I would also like to express my gratitude to the alumni of the Particle Physics Laboratory at Okayama University.
In particular, my colleagues, Ryo~Okada and Wenjie~Ma, gave me emotional support as I pursued my study.\\
\hs
In addition to that, I have been indebted to many people throughout my life.
I believe that the reason I am able to spend such a meaningful time now is because of the encounters I have had with each and every one of you.\\
\hs
Finally, I would like to thank my family from the bottom of my heart for supporting me.\\
\hs
This work was supported by JSPS KAKENHI Grant Number JP22KJ2301.
\vspace{\stretch{2}}
\thispagestyle{empty}
